---
title: "Simulation"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(rvest)

set.seed(1)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

```

Load key packages and source necessary files.
```{r}
library(tidyverse)
source("source/sim_mean_sd.R")
```


We can "simulate" by running our function.

```{r}
sim_mean_sd(n_subj = 400)
```


Can I "verify" the Central Limit Theorem?

First with a `for` loop

```{r}
output = vector("list", length = 100)

for (i in 1:100) {
  
  output[[i]] = sim_mean_sd(30)
}

output |> 
  bind_rows() |> 
  ggplot(aes(x = mu_hat)) +
  geom_density()
```


Try to repeat with a `map` statement


```{r}
sim_results_df =
  expand_grid(
    iter = 1:1000,
    sample_size = c(30, 60, 90, 120)
  ) |> 
  mutate(
    results = map(iter, sim_mean_sd)
  ) |> 
  unnest(results)
```


Let's look at this:

Making a violin plot of sample size vs. mean
```{r}
sim_results_df |> 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)
  ) |> 
  ggplot(aes(x = sample_size, y = mu_hat)) +
  geom_violin()
```


Let's try to summarize...

```{r}
sim_results_df |> 
  group_by(sample_size) |> 
  summarize(
    emp_mean = mean(mu_hat),
    emp_se = sd(mu_hat)
  )
```


## Simple linear regression

```{r}
sim_df =
  tibble(
    x = rnorm(30, mean = 1, sd = 1),
    y = 2 + 3 * x + rnorm(30, 0, 1)
  )

sim_df |> 
  ggplot(aes(x = x, y = y)) +
  geom_point()

slr_fit = lm(y ~ x, data = sim_df)

coef(slr_fit)
```


Turn this into a function

```{r}
sim_regression = function(n_subj, beta_0 = 2, beta_1 = 3) {
  
  sim_df =
  tibble(
    x = rnorm(n_subj, mean = 1, sd = 1),
    y = beta_0 + beta_1 * x + rnorm(n_subj, 0, 1)
  )
  
  slr_fit = lm(y ~ x, data = sim_df)
  
  tibble(
    beta0_hat = coef(slr_fit)[1],
    beta1_hat = coef(slr_fit)[2]
  )
}

```

```{r}
sim_regression(n_subj = 30)
```

Using `for` loops

```{r}
output = vector("list", length = 500)

for (i in 1:500) {
  
  output[[i]] = sim_regression(n_subj = 30)
}

output |> 
  bind_rows()
```


Using`maps` instead.

```{r}
slr_sim_results_df =
  expand_grid(
    sample_size = 30, 
    iter = 1:500
  ) |> 
  mutate(
    results = map(sample_size, sim_regression)
  ) |> 
  unnest(results)

slr_sim_results_df |> 
  ggplot(aes(x = beta0_hat, y = beta1_hat)) +
  geom_point()
```


## One more example !!


Jeff gave example of "birthday problem"

```{r}
birthdays = sample(1:365, 5, replace = TRUE)
```

* `sample`: what are you sampling from, how many samples are you taking
* `replace = TRUE`: if you pick 17 first, you can also pick 17 later

Is there a repeated birthday?

```{r}
unique(birthdays) < 5

length(unique(birthdays)) < 5

repeated_bday = length(unique(birthdays)) < 5

repeated_bday
```

* `unique`: what are the unique values (e.g. birthdays) that show up in the vector
* `length`: if there's repeat then it will be TRUE, if not, it's FALSE

Put this in a function

```{r}
bday_sim = function(n_room) {
  
  birthdays = sample(1:365, n_room, replace = TRUE)
  
  repeated_bday = length(unique(birthdays)) < n_room

  repeated_bday
  
}

bday_sim(20)
```


```{r}
bday_sim_results =
  expand_grid(
    bdays = 5:50,
    iter = 1:2500
  ) |> 
  mutate(
    result = map_lgl(bdays, bday_sim)
  ) |> 
  group_by(
    bdays
  ) |> 
  summarize(
    prob_repeat = mean(result)
  )
```

`map_lgl`: logic every single time (e.g. TRUE, FALSE)


Plot this

```{r}
bday_sim_results |> 
  ggplot(aes(x = bdays, y = prob_repeat)) +
  geom_point() +
  geom_line()
```

